\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{datetime}
\usepackage{hyperref}
\usepackage[a4paper, margin=2cm]{geometry}

\newdateformat{monthyeardate}{\monthname[\THEMONTH] of \THEYEAR}

\pagestyle{empty}
\setlength{\parindent}{0pt}

\begin{document}

\begin{center}
  {\Large \textbf{Francisco Figari}} \\[4pt]
  Buenos Aires based Software Developer \\[2pt]
  {\small \href{mailto:figafran@gmail.com}{figafran@gmail.com} -- \href{https://www.linkedin.com/in/ffigari}{linkedin.com/in/ffigari}} \\[2pt]
  {\small \textit{Resume} -- \monthyeardate\today}
\end{center}

\vspace{0.5em}

\section*{Professional Summary}

With ~9 years of experience in the software industry, I build software that
balances stakeholders' needs with technical quality. Experienced in multiple
programming languages, I easily adapt to new codebases. Having worked across
diverse domains (fintech, urbanism, neuroscience) and team structures, I bring a
domain-independent approach to building software that adapts to each project's
specific needs.

\section*{Relevant Experience}

\textbf{Technical Leader @ Urbanly} \hfill August 2025 -- present
\begin{itemize}
  \item Built real estate housing market simulation prototype within three
    months of joining. Applied SOLID principles to build core components
    which were then developed by the rest of the team. Designed system to
    incorporate both CEO and external client requirements. Built with
    \texttt{TypeScript} and \texttt{Web Workers}, leveraging geospatial
    algorithms (oriented bounding box) and formats (\texttt{GeoJSON}).
  \item Refactored project structure to allow reuse of code in both browser and
    CLI versions of the system. Introduced unit testing across standalone
    modules of the project.
  \item Continuously deployed prototype for client assessment. Worked side by
    side with clients to define requirements. Travelled overseas to meet in
    person with clients, present progress, design specifications, and plan
    improvements.
  \item Generated multiple \texttt{HTML} reports to showcase improvements of the
    simulation. Used dataframes and \texttt{PlotlyJS} to standardize analysis of
    simulations' results.
  \item Mentored 4 junior developers into adopting better development practices.
    Reviewed their work by giving constructive feedback.
\end{itemize}

\textbf{Backend Developer @ Brubank} \hfill April 2023 -- August 2025
\begin{itemize}
  \item Developed within a ~30-service microservices ecosystem (our team was in
    charge of ~8 of them; ~200 requests per second in the biggest one). Set up
    both new web APIs and new \texttt{Azure Service Buses} using company's
    infrastructure. Used \texttt{Golang}.
  \item Extracted logic out of foundational monolithic service. Worked with
    external providers' APIs.
  \item Used monitoring tooling (\texttt{Datadog}) to validate no errors occurred with
    newly deployed features. Coordinated multi-service deployments to ensure
    inter-service dependencies were kept up and running at all times. Applied
    feature flags and feature rollouts to achieve controlled deployments.
  \item Built new investment features like CEDEARs buying and selling.
    Maintained existing ones like time deposits. Assessed feasibility of
    Argentinian bonds features by testing provider's API and our existing
    implementation, which resulted in a product document used by a junior
    developer to build the feature while I mentored him.
  \item Defined \texttt{GraphQL} interfaces used between backend and mobile team.
    Coordinated building of RFC documents with whole team (mobile + QA +
    backend). Ensured backward compatibility across all developments,
    particularly for older mobile versions.
\end{itemize}

\textbf{Research Intern @ LIAA, DC, FCEyN, UBA} \hfill August 2021 -- September 2022
\begin{itemize}
  \item Worked with neuroscientist to build web browser eye tracker aimed to
    allow remote clinical studies. Built using \texttt{JavaScript} and event-based
    programming. Used \texttt{JavaScript} libraries (\texttt{jsPsych},
    \texttt{WebGazer}) from the neuroscience ecosystem. Reviewed related
    scientific literature.
  \item Adapted implementation for consumer-grade webcams, integrating
    calibration routines to compensate for the lack of head stabilization in
    remote settings, unlike controlled lab environments. Validated accuracy
    by replicating the known neuroscience ``antisaccades'' task and running a
    remote study with 20 participants. Collected and studied data using
    \texttt{Python} and \texttt{Pandas}.
\end{itemize}

\textbf{Lead Programmer @ UrbanSim} \hfill July 2018 -- November 2020
\begin{itemize}
  \item Worked with urbanists to develop multi-family affordable housing
    procedural generator in \texttt{C++}. Implemented different heuristics (e.g., greedy
    search, brute force) to maximize dwelling-unit count while ensuring urban
    planning constraints were satisfied. Continuously refactored and extended
    codebase to account for a growing set of constraints.
  \item Extended surrounding web platform alongside other developers by using
    \texttt{Python} in the backend and \texttt{JavaScript} in the frontend.
    Developed geospatial visualizations of the procedural generator's results.
\end{itemize}

\section*{Skills}

\textbf{Languages \& Frameworks:} \texttt{Golang}, \texttt{TypeScript},
\texttt{Python}, \texttt{C++}, \texttt{NodeJS}, \texttt{React}, \texttt{Pandas}
\\

\textbf{Infrastructure:} microservices, \texttt{Azure Service Bus},
\texttt{REST} APIs, \texttt{Datadog} \\

\textbf{Data:} \texttt{PostgreSQL}, \texttt{Redis} \\

\textbf{Practices:} SOLID, unit/integration testing, refactoring, feature flags,
CI/CD \\

\textbf{Domains:} fintech, geospatial/urbanism, neuroscience \\

\textbf{Spoken languages:} Spanish (native), English (professional), French
(schooling)

\section*{Education and Training}

\begin{itemize}
  \item Product Discovery for Agile Teams @ \textit{Sense and Respond Learning}; 8 hours, intro to \textit{Lean Product Canvas}.
  \item \textit{Licenciatura} in Computer Science @ \textit{DC, FCEyN, UBA}, equivalent to Bachelor + Master with thesis, started in 2013 and finished in 2022.
  \item High school @ \textit{Lyc\'{e}e Jean Mermoz, Buenos Aires}, finished in 2013.
\end{itemize}

\end{document}
