\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{datetime}
\usepackage{hyperref}
\usepackage[a4paper, margin=2cm]{geometry}

\newdateformat{monthyeardate}{\monthname[\THEMONTH] of \THEYEAR}

\pagestyle{empty}
\setlength{\parindent}{0pt}

\begin{document}

\begin{center}
  {\Large \textbf{Francisco Figari}} \\[4pt]
  Buenos Aires based Tech Leader \\[2pt]
  {\small \href{mailto:figafran@gmail.com}{figafran@gmail.com} -- \href{https://www.linkedin.com/in/ffigari}{linkedin.com/in/ffigari}} \\[2pt]
  {\small \textit{Resume} -- \monthyeardate\today}
\end{center}

\vspace{0.5em}

\section*{Professional Summary}

With ~9 years of experience in the software industry, I bridge product and
technical needs into a coherent vision which allows for short cycles of ship,
sense and respond. Having worked in different domains (fintech, urbanism,
neuroscience, software factory), I have become capable of translating open-ended
questions into structured backlog which considers both the stakeholders' needs
and the difficulties inherent to scaling a codebase.

\section*{Relevant Experience}

\textbf{Technical Leader @ Urbanly} \hfill August 2025 -- present
\begin{itemize}
  \item Gathered requirements and led design and implementation of core
    components of a housing market simulation PoC. Kept tracking specs from the
    client and building backlog to guide further development.
  \item Simultaneously tracked client needs while aligning with the CEO's
    vision of the product, effectively incorporating both views into the
    system.
  \item Mentored development team into adopting better development practices
    (e.g., dependency inversion principle, single responsibility classes, basic
    unit testing).
  \item Traveled overseas to meet with clients, present project progress,
    gather feedback, and plan future work.
\end{itemize}

\textbf{Backend Developer @ Brubank} \hfill April 2023 -- August 2025
\begin{itemize}
  \item As a member of the investments team, I led discovery of ``Buying and
    Selling of Argentinian Stocks'' feature (i.e., tested provider's API, studied
    how to extend the existing implementation) and built product document which
    was then used by another member of the team to develop the actual feature
    with me only having to mentor him.
  \item Implemented new features (e.g., buying and selling of CEDEARs),
    maintained existing ones (e.g., time deposits) and migrated monolith
    sections into new microservices.
  \item Defined mobile to backend interfaces on various occasions, which
    ensured smooth collaboration between technology teams.
  \item Collaborated with QA team to ensure features were properly tested
    before production deployment.
  \item Using system metrics (Datadog) and feature flags, I was able to
    both verify the validity of new developments and deploy incrementally.
\end{itemize}

\textbf{Research Intern @ LIAA, DC, FCEyN, UBA} \hfill August 2021 -- September 2022
\begin{itemize}
  \item In the context of my ``Licenciatura'' thesis, I collaborated with neuroscientists to build a web eye
    tracker meant for clinical studies.
  \item Studied researchers' use cases to understand the right tool to build.
  \item Studied feasibility of the project by reading state-of-the-art papers
    and existing implementations.
  \item Carried out clinical experiments to test out the implementation's performance.
\end{itemize}

\textbf{Lead Programmer @ UrbanSim} \hfill July 2018 -- November 2020
\begin{itemize}
  \item Tracked down urban planning constraints alongside urbanists to progressively
  implement an affordable multi-housing procedural generator.
  \item Led a small team of 2 developers in related procedural system and in the web
    platform built around it.
\end{itemize}

\section*{Key Competencies}

\subsection*{Product \& Delivery}
\begin{itemize}
  \item Ability to empathize with stakeholders' vision and understand desired direction of growth.
  \item Capable of building a robust backlog which tracks product needs while also taking into
    account the underlying implementation.
  \item Focused on short build-ship cycles to obtain quick feedback loops.
  \item Ability to approach open-ended questions and create comprehensive plans of
  actions which can be distributed across the development team.
\end{itemize}

\subsection*{Technical Fluency}
\begin{itemize}
  \item Skilled in translating problems described in natural language into
    formal representations.
  \item Experience with multiple programming languages (Typescript, Golang,
    Python, C++) and paradigms (OOP, procedural programming, event-based).
  \item General knowledge of microservices ecosystems, REST APIs and persistence.
  \item Effective usage of AI agents (e.g., Claude Code) to speed up
    development processes.
  \item Capable of designing interfaces used by different technologies.
  \item Ability to scale codebases, perform refactoring and decompose big flows
    into smaller manageable subflows.
  \item Usage of metrics systems like Datadog.
\end{itemize}

\subsection*{Leadership \& Collaboration}
\begin{itemize}
  \item Capable of tracking working context of different members of the team, which
  allows me to assign work strategically. Capable of leading small teams.
  \item Identified and resolved blockers between team members.
  \item Comfortable with Agile methodologies like Scrum or Kanban.
  \item Interdisciplinary worker: experience with urban planners, architects,
    neuroscientists, economists; experience with frontend, backend and mobile
    developers and project managers.
  \item Trilingual speaker: native Spanish, schooling in French and English at work.
\end{itemize}

\section*{Education and Training}

\begin{itemize}
  \item Product Discovery for Agile Teams @ \textit{Sense and Respond Learning}; 8 hours, intro to \textit{Lean Product Canvas}.
  \item Yoga teaching training program @ \textit{Red Prisma} between July 2023 and April 2025. 18 intensive weekends plus weekly theoretical classes.
  \item \textit{Licenciatura} in Computer Science @ \textit{DC, FCEyN, UBA}, equivalent to Bachelor + Master with thesis, started in 2013 and finished in 2022.
  \item High school @ \textit{Lycée Jean Mermoz, Buenos Aires}, finished in 2013.
\end{itemize}

\end{document}
